---
title: "Lesson 1 - ggplot Examples"
author: "DS705"
date: "1/14/2018"
output:
  html_document: default
  pdf_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(DS705data)
require(ggplot2)
require(gridExtra)
```

## Histogram

```{r, fig.height=3,fig.width=4,fig.align='center'}
# you can play with fig.height and fig.width to adjust the size
data(HealthExam)
Men <- HealthExam[HealthExam$Sex=="M",]
ggplot( Men, aes( x = Height) ) + 
  geom_histogram( binwidth = 2,
                  colour = "black",
                  fill = "darkseagreen2")
```

You can and should play with the `binwidth` parameter to find a value that nicely summarizes the data.

## Histogram with normal density curve

```{r, fig.height=3,fig.width=4,fig.align='center'}
ggplot( Men,  aes( x = Height)) + 
  geom_histogram( aes( y = ..density..),
                 binwidth = 2,
                 colour = "black",
                 fill = "darkseagreen2") + 
  stat_function( fun = dnorm,
                 args = list( mean = mean(Men$Height),
                              sd = sd(Men$Height)))
```

## Boxplot

```{r, fig.height=3,fig.width=4,fig.align='center'}
ggplot( data = Men, aes( x = "", y = Height)) + 
  geom_boxplot() + 
  labs( x = "Men")
```

A single boxplot isn't very exciting.  As we'll see later we often use a boxplot to compare quantitative data for multiple groups, e.g. heights of men and women like this:

```{r, fig.height = 3, fig.width = 4, fig.align = 'center'}
ggplot(data = HealthExam, aes( x = Sex, y = Height)) + 
  geom_boxplot()
```

## Putting plots side-by-side and adding color

```{r, fig.align = 'center'}
plot1 <- ggplot( data = Men, aes( x = "", y = Height)) + 
  geom_boxplot( colour = "black",
                fill = "darkseagreen2") + 
  labs( x = "Men")

plot2 <- ggplot( data = Men, aes( x = "", y = Cholesterol)) + 
  geom_boxplot( colour = "black",
               fill = "plum2") + 
  labs( x = "Men")

grid.arrange( plot1, plot2, ncol = 2)
```

A nice chart of pre-defined colors for use in ggplot2 can be found here:

http://sape.inf.usi.ch/quick-reference/ggplot2/colour
